---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timecardassistant

<!-- badges: start -->
<!-- badges: end -->

The goal of timecardassistant is to create an efficiency around time tracking and 
help develop a comfort level of workign with R.

## Installation

You can install the released version of timecardassistant from 
[GitHub](https://github.com/benrwoodard/timecardassistant.git) with:

``` r
# install.packages("devtools")
devtools::install_github("benrwoodard/timecardassistant")
```
## Example

This is a basic example which shows you how to record your time:

```{r example}
library(timecardassistant)

starttc('clientname', 'project name')

```

If you have missed the time when you started and want to start the activity to a previous time then you simply use the 'started' argument.

Each hour is calculated as 100% or 1. To set the time to be exactly 30 minutes before the curren time you would run the following:

```{r started}
starttc('clientname', 'project name', started = .5)
```

Here is a helpful breakdown of the hour break points:

Minutes | Percent |
------- | ------- |
55 | .92 |
50 | .83 |
45 | .75 |
40 | .67 |
35 | .58 |
30 | .5 |
25 | .42 |
20 | .33 |
15 | .25 |
10 | .17 |
5 | .08 |

## When the activity is done

To record the acitity time to the 'timecard' object you will use the `donetc()` function
```{r donetc_basic}
donetc()
```

### Retroactive activity completion

If you need to adjust the time when the last recorded activity was finished then you will add the 'finished' argument value.
```{r done_retroacive}
donetc(finished = .5)
```

### Activity Notes

Adding notes is a good idea if the project name is not sufficient to record your activity or followup actions need to be recorded.
```{r done notes}
donetc(notes = 'this will be recorded with the activity record')
```


The resulting 'timecard' object will looks something like this:
```{r timecardexample}
## Load Example Data
starttc('clientname', 'project name', .5)
donetc(notes = 'this is just a test')

starttc('clientname2', 'project 2', 1.5)
donetc(1)

starttc('clientname', 'project 3', 2.5)
donetc(1.5, notes = 'this is just a test')
```


```{r example_view}
timecard
```



