---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timecardassistant

<!-- badges: start -->
<!-- badges: end -->

The goal of timecardassistant is to create an efficiency around time tracking and 
help develop a comfort level of workign with R.

## Installation

You can install the released version of timecardassistant from 
[GitHub](https://github.com/benrwoodard/timecardassistant.git) with:

``` r
# install.packages("devtools")
devtools::install_github("benrwoodard/timecardassistant")
```
## Example

This is a basic example which shows you how to record your time:

```{r example}
library(timecardassistant)
## Load Example Data
load('data/tc_example.RData')
timecard <- ex

starttc('clientname', 'project name')

```

If you have missed the time when you started and want to start the activity to a previous time then you simply use the 'started' argument.

Each hour is calculated as 100% or 1. To set the time to be exactly 30 minutes before the curren time you would run the following:

```{r started}
starttc('clientname', 'project name', started = .5)
```

Here is a helpful breakdown of the hour break points:

Minutes | Percent |
------- | ------- |
30 | .5 |
25 | .42 |
20 | .33 |
15 | .25 |
10 | .17 |
5 | .08 |


