---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timecardassistant

<!-- badges: start -->
<!-- badges: end -->

The goal of timecardassistant package is to create efficiency around time tracking along with helping improve the end users comfort level of working with R.

## Installation

You can install the released version of timecardassistant from 
[GitHub](https://github.com/benrwoodard/timecardassistant.git) with:

``` r
# install.packages("devtools")
devtools::install_github("benrwoodard/timecardassistant")
```
## Examples

### Start activity record

This is a basic example which shows you how to record your time:

```{r example}
library(timecardassistant)

starttc('clientname', 'project name')
```

This function creates a 'ps' object which is used in the `donetc()` function to create the final record for the activity on the 'timecard' object.

#### Adjusting activity started time

If you have missed the time when you started and want to start the activity to a previous time then you simply use the 'started' argument.

Each hour is calculated as 100% or 1. To set the time to be exactly 30 minutes before the current time you would run the following:

```{r started}
starttc('clientname', 'project name', started = .5)
```

Here is a helpful breakdown of the hour break points:

minutes | started |
------- | ------- |
55 | .92 |
50 | .83 |
45 | .75 |
40 | .67 |
35 | .58 |
30 | .5 |
25 | .42 |
20 | .33 |
15 | .25 |
10 | .17 |
5 | .08 |

### Finished activity record

To record the activity time to the 'timecard' object you will use the `donetc()` function
```{r donetc_basic}
donetc()
```

#### Adjusting activity completed time

If you need to adjust the time when the last recorded activity was finished then you will add the 'finished' argument value.
```{r done_retroacive}
donetc(finished = .5)
```

#### Adding activity notes

Adding notes is a good idea if the project name is not sufficient to record your activity or followup actions need to be recorded.
```{r done notes}
donetc(notes = 'this will be recorded with the activity record')
```

#### Timecard csv file created

Every time you use the `donetc()` function a csv file is created with the 'yyyy-mm-dd_timecard.csv' naming convention. There is only one file per day and can be used to restore the timecard object if needed, using the `restoretc()` function.

### Example Workflow

The following is an example of a project activity workflow. Normally, these would be added in the console and not recorded in an R script file since these are simply triggers to recorded the start and end of an activity.
```{r timecardexample}
## Load Example Data
starttc('clientname', 'project 1', .5)
donetc(notes = 'this is just a test')

starttc('clientname2', 'project 2', 1.5)
donetc(1)

starttc('clientname', 'project 3', 2.5)
donetc(1.5, notes = 'this is just a test')
```

#### Products of the functions

The preceding functions will create the 'timecard' object and the timecard csv file for the date the functions were called.
```{r object_view}
timecard
```


```{r csv_view}
list.files(pattern = "_timecard.csv")
```



